Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2016-12-07 Master Thesis/synopsis.tex
Remark on Kronecker dimension
Add some proof for 4.3

@@

\paragraph{} Let $n\in\mathbb{N}$. For all intermediate fields $L$ of $\overline{K}/K$, $\sigma$ induces an isomorphism:
\[ \varphi_n:L'^\times/n \cong\mathrm{H}^1(L', \mu_n) \to \mathrm{H}^1(L,\mu_n) \cong L^\times/n \]
Obviously, for intermediate fields $L\subset M$ of $\overline{K}/K$ the following diagram commutes:
\[ \begin{tikzcd}
L'^\times/n \ar[r, "\varphi_n"]\dar & L^\times/n \dar\\
M'^\times/n \ar[r, "\varphi_n"'] & M^\times/n
\end{tikzcd} \]
Let $P\in X_0$ and $v_P:K\to\mathbb{Z}\cup\{\infty\}$ be the corresponding discrete normalized valuation and let $U_P$ be the group of units of the valuation ring $\mathcal{O}_P$. We denote the natural projection $U_P\to k(P)^\times,\ x\mapsto x\mod P$ by $r_P$. For $n\in\mathbb{N}$ the following sequence is exact, since valuation rings are integrally closed:
\[ 0\longrightarrow U_P/n\longrightarrow K^\times/n\longrightarrow\mathbb{Z}/n\mathbb{Z}\longrightarrow 0 \]
We'll use the same notation for $P' = \sigma(P)\in X'_0$.

@@

>>>>

\begin{remark}
A one-dimensional finitely generated field over its prime field is just a global field. A two-dimensional finitely generated field over $\mathbb{Q}$ is a function field in one variable over $\mathbb{Q}$.
\end{remark}

@@

\paragraph{} Let $n\in\mathbb{N}$. In the previous remark, we have determined that the following diagram commutes: 
\[ \begin{tikzcd}
G_K \ar[r]\ar[d, "\sigma"'] & G_k\\
G_{K'}\ar[ru]
\end{tikzcd} \]
Now the operation of $G_K$ and $G_{K'}$ on $\mu_n$ factors through $G_k$, thus we have $\sigma(g)\xi = g\xi$ for all $\xi\in\mu_n$ and $g\in G_K$. Therefore, for all intermediate fields $L$ of $\overline{K}/K$, $\sigma$ induces an isomorphism:
\[ \varphi_n:L'^\times/n \cong\mathrm{H}^1(L', \mu_n) \to \mathrm{H}^1(L,\mu_n) \cong L^\times/n \]
Obviously, for intermediate fields $L\subset M$ of $\overline{K}/K$ the following diagram commutes:
\[ \begin{tikzcd}
L'^\times/n \ar[r, "\varphi_n"]\dar & L^\times/n \dar\\
M'^\times/n \ar[r, "\varphi_n"'] & M^\times/n
\end{tikzcd} \]
Let $P\in X_0$ and $v_P:K\to\mathbb{Z}\cup\{\infty\}$ be the corresponding discrete normalized valuation and let $U_P$ be the group of units of the valuation ring $\mathcal{O}_P$. We denote the natural projection $U_P\to k(P)^\times,\ x\mapsto x\mod P$ by $r_P$. For $n\in\mathbb{N}$ the following sequence is exact, since valuation rings are integrally closed:
\[ 0\longrightarrow U_P/n\longrightarrow K^\times/n\longrightarrow\mathbb{Z}/n\mathbb{Z}\longrightarrow 0 \]
We'll use the same notation for $P' = \sigma(P)\in X'_0$.

@@

\begin{proof}
\begin{enumerate}[(i)]
\item  We have $(K^\text{t}_P)^\times/n\cong \mathbb{Z}/n\mathbb{Z}$ since $\operatorname{char}k(P) = 0$. The canonical map $K^\times\to (K^\text{t}_P)^\times/n$ can be identified with the map $K^\times /n\to\mathbb{Z}/n$ induced by $v_P$. Now the following commutative diagram gives us the result:
\[ \begin{tikzcd}
0 \ar[d] & 0 \ar[d]\\
U_{P'}/n \ar[r, dashed]\ar[d] & U_P/n\ar[d]\\
K'^\times /n \ar[r, "\varphi_n"]\ar[d] & K^\times/n\ar[d]\\
(K^\text{t}_P)'^\times /n \ar[r, "\varphi_n"'] &  (K^\text{t}_P)^\times /n
\end{tikzcd} \]
\item Consider the field extension $K_P/K$
\end{enumerate}
\end{proof}
